Association between Breast Cancer and Hepatitis C Virus with Age Controlling

### 2022-12-06 manuscript/manuscript.tex
fixed equation

This paper will explore the risk factors associated with breast 
cancer in women. Breast cancer is extremely prevalent and researchers 
are constantly trying to determine risk factors to identify women for preventative exams.
There are many studies attempting to determine if there is an association 
between certain risk factors and breast cancer including chronic hepatitis 
C infection \citep{Larrey2010is} and hepatitis B \citep{vishnu2016does}.

Specifically, this paper will examine if there is an association between 
testing positive for hepatitis C virus and breast cancer while controlling 
for age in Egyptian populations. Both Hepatitis C and breast 
cancer are extremely prevalent in Egypt \citep{Hussein2021high}.
Additionally, research has found that women who are seropositive for 
HCV have more agressive forms of breast cancer. However, there is 
minimal research concerning the effect of age on the associaiton.

Recently on October 6th, Egypt and Qatar agreed to collaborate in the health sector and 
use each other's expertise. The health ministers specifically mentioned research 
in Hepatitis C and breast cancer as an area of interest \citep{arham2022egypt}. 
This meeting emphasizes the importance of diving into Hepatitus C Virus 
and it's association with breast cancer. There have been conflicting
foundings so studies should indenify additional variables that could 
contribute to better understanding the relationship. For that reason,
this paper is focusing on controlling for age of female patients.

@@

The data used in this paper is from a 2020 retrospective case-control 
study based on Egyptian female populations \citep{2020association},
sponsered by Mansoura University in Egypt.

The study group consists of 405 patients treated at the Oncology Center 
- Mansoura University in the past 10 years. In order to be included, 
invasive breast cancer must be biopsy-proven. Patients with unknown 
viral marker status, multiple cancer diagnoses and virus-unrelated 
hepatic pathology were all excluded.

The control group consists of 
data from a previous study, conducted from 2015-2017. There are 145 
females from the same geographic distribution, all with no previous 
cancer diagnosis. In both groups, all patients are above the age of 
18. For this paper, patients are stratified based on age- older patients 
are considered 45 years or above and younger patients are below 45 years. 
The data is summarized in the following 2x2 contingency tables.

\begin{center}
  \captionof{table}{2x2 Contingency Table for all patients}
\label{tab:all}
\begin{tabular}{rrrr}
  \toprule
  & Breast Cancer & No Cancer Diagnosis & Total\\ 
  \midrule
  HCV Seropositive & 88 & 15 & 103 \\ 
  HCV Seronegative & 317 & 130 & 447 \\ 
  \midrule
  Total & 405 & 145 & 550 \\ 
  \bottomrule
\end{tabular}
\end{center}

\begin{center}
  \captionof{table}{2x2 Contingency Table for pateints younger than 45}
\label{tab:younger}
\begin{tabular}{rrrr}
  \toprule
  & Breast Cancer & No Cancer Diagnosos & Total\\
  \midrule
  HCV Seropositive & 17 & 2 & 19 \\ 
  HCV Seronegative & 110 & 91 & 201 \\ 
  \midrule
  Total & 127 & 93 & 220 \\ 
  \bottomrule
\end{tabular}
\end{center}

\begin{center}
  \captionof{table}{2x2 Contingency Table for pateints older than 45}
\label{tab:older}
\begin{tabular}{rrrr}
  \toprule
  & Breast Cancer & No Cancer Diagnosos & Total\\
  \midrule
  HCV Seropositive & 71 & 13 & 84 \\ 
  HCV Seronegative & 207 & 39 & 246 \\
  \midrule 
  Total & 278 & 52 & 330 \\ 
  \bottomrule
\end{tabular}
\end{center}

>>>>

Breast cancer is the world's most prevalent cancer and occurs in 
every country in women at any age after puberty. Therefore,
it's extremely important to determine certain risk factors 
that can help detect breast cancer early and save lives. Research 
is constantly being performed to identify risk factors from lifestyle
factors to genetics \citep{sun2017risk}. Family history is shown to 
be a strong predictor for women developing breast cancer.

However, recent research is looking into how certain diseases can be a risk 
factor for breast cancer or increase the agression of the cancer. 
Research by the Department of Endocrine and Breast Surgery in China 
focused on Hepatitis B and it's association with breast cancer and found 
HBV is potentially affecting estrogen levels, potentially leading 
to a new way of screening for women \citep{vishnu2016does}. Additionally,
some work has been done with Hepatitis C seropositivity in France, but 
the control group was women with other liver diseases \citep{Larrey2010is}.
Thus, the results can only compare women with certain liver diseases, such as 
hepatitis B, alcoholic liver disease, and hemochromatosis to 
women with Hepatitis C.

Egypt in particular has the highest prevalence of Hepatitis C, and breast 
cancer is the most common cancer. Thus, an association between the two 
would be extremely benficial. So, this paper will examine if there is an 
association between testing positive for hepatitis C virus and breast cancer 
diagnosis while controlling for age in Egyptian populations. Age is a knwon 
and accepted risk factor of breast cancer; older women are more likely to 
develop tumors \citep{sun2017risk}. Therefore, controlling for age is necessary.

Inconsistency of Hepatitis C prevalence in different regions of Egypt makes 
it difficult to generalize research to the entire country. This paper will 
focus on a small region within the country with high 
prevalence \citep{Hussein2021high} and make conclusions relevent to a specific 
subgroup.

Recently on October 6th of 2022, Egyptian Minister of Health Abdel-Ghaffar and 
Qatari Minister of Health Hanan Al-Kuwari met in Doha and agreed to use each 
other's expertise in the health field. The health ministers specifically mentioned research 
in Hepatitis C and breast cancer as an area of interest \citep{arham2022egypt}. 
This meeting emphasizes the importance of diving into Hepatitus C Virus 
and it's association with breast cancer. The Egyptian government has defined 
breast cancer as an area of concern and desires to conduct research within their 
population, which is very minimal at the moment.

@@

The data used in this paper is from a 2020 retrospective case-control 
study based on Egyptian female populations \citep{hussein2020association},
sponsered by Mansoura University in Egypt. The study was conducted with
several goals. The main goals we are interested in are 1. to test if seropositivity
is associated with breat cancer diagnosis in Egyptian population and 
2. to test if HCV-positive patients harbour more agressive breast tumors 
than HCV-seronegative patients.

The study group consists of 405 patients treated at the Oncology Center 
- Mansoura University in the past 10 years. The data was retrieved from
the hosipital filing system. In order to be included, the patients'
invasive breast cancer must be biopsy-proven. Patients with unknown 
viral marker status, multiple cancer diagnoses and virus-unrelated 
hepatic pathology were all excluded. Additionally, the study measured
two outcome measures. The primary measure was the prevalence of 
HCV seropisitivity, which is defined as being Seropositive for the duration
of the study, an average of 6 months. The secondary outcome measure was
the number of disease related events related to breast cancer diagnosis. 
Disease-free survival was calculated from the time of diagnosis to the
last date of follow up for the study.

The control group consists of 
data from a previous study, conducted from 2015-2017. There are 145 
females from the same geographic distribution, all with no previous 
cancer diagnosis. The group consists of healthy volunteers or hosipital
patients with no cancer diagnosis.

In both groups, all patients are above the age of 
18. The ratio of study-to-control was intended to be 1:3.
For this paper, patients are stratified based on age- older patients 
are considered 45 years or above and younger patients are below 45 years. 
The data is summarized in Table~\ref{tab:all}.

\begin{table}[!h]
  \begin{center}
  \captionof{table}{2x2 Contingency Table for all patients}
\label{tab:all}
\begin{tabular}{rrrr}
  \toprule
  & Breast Cancer & No Cancer Diagnosis & Total\\ 
  \midrule
  HCV Seropositive & 88 & 15 & 103 \\ 
  HCV Seronegative & 317 & 130 & 447 \\ 
  \midrule
  Total & 405 & 145 & 550 \\ 
  \bottomrule
\end{tabular}
\end{center}
\end{table}

\begin{table}[!h]
  \begin{doublespace}
    Of the 550 women who were involved in the study, 220 were below 
the age of 45 and 330 were of age 45 or above. Table~\ref{tab:younger} 
and Table~\ref{tab:older} show the break down of seropositivity and 
seronegativity for the stratified age groups.
  \end{doublespace}
  \begin{center}
  \captionof{table}{2x2 Contingency Table for pateints younger than 45}
\label{tab:younger}
\begin{tabular}{rrrr}
  \toprule
  & Breast Cancer & No Cancer Diagnosos & Total\\
  \midrule
  HCV Seropositive & 17 & 2 & 19 \\ 
  HCV Seronegative & 110 & 91 & 201 \\ 
  \midrule
  Total & 127 & 93 & 220 \\ 
  \bottomrule
\end{tabular}
\end{center}
\end{table}

\begin{table}[!htb]
\begin{center}
  \captionof{table}{2x2 Contingency Table for pateints 45 and older}
\label{tab:older}
\begin{tabular}{rrrr}
  \toprule
  & Breast Cancer & No Cancer Diagnosos & Total\\
  \midrule
  HCV Seropositive & 71 & 13 & 84 \\ 
  HCV Seronegative & 207 & 39 & 246 \\
  \midrule 
  Total & 278 & 52 & 330 \\ 
  \bottomrule
\end{tabular}
\end{center}
\end{table}
